Partial MILP to improve $\alpha,\beta$-CROWN accuracy \\ for hard DNN verification instances

### 2024-09-16 ICLR25/Paper_noProof.tex
abstract
table in main doc

>>>>

\section*{Tables}

The following table are the results of running $\alpha,\beta$-Crown pure BaB mode with different timeout for different networks. The numbers shown in the table is the rate of images in percentage.

\begin{tabular}{||c|c|c||c|c|c||}
	\hline
	Network & Acc & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
	Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline

	MNIST 6$\times$100 & 96\% & 90\% & 33\% & 35\% & 40\%   \\
	$\epsilon = 0.026$ &  &  & ? &  18s &  1600s  \\  \hline
    MNIST 6$\times$200 & 97\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
	$\epsilon = 0.015$ & &  & ? &  17s &  ?s  \\  \hline
	MNIST 9$\times$100 & 95\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
	$\epsilon = 0.026$ &  &  & ? &  20s &  ?s  \\  \hline
	MNIST 9$\times$200 & 95\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
	$\epsilon = 0.015$ & &  & 7s &  s &  ?s  \\  \hline
	MNIST 6$\times$500 &  ? & 94\%  & 41\%  & 43\%  & 44\%   \\ 
	$\epsilon = 0.035$ & &  & 6s &  15s &  1002s  \\  \hline
	CIFAR CNN-B-adv & ?  & 62\%  &  ? & 40\%  & 42\%   \\
	 &  &  & s & s & s  \\ \hline \hline
	CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
	Wong &  &  & 2s & 2s & 2s  \\ \hline

\end{tabular}

\vspace*{4ex}
\begin{tabular}{|c|c|c|}
	\hline
	Verifier & Rate & Average time \\ \hline
	Marabou & 0 & 0 \\ \hline
	$\alpha,\beta$-Crown & 0 & 0 \\ \hline
	Full MILP & 0 & 0 \\ \hline
	0 & 0 & 0 \\ \hline
\end{tabular}

\vspace*{4ex}

The table of undecided images among first 100 images in database by different methods for different network.

\begin{tabular}{|c|c|c|c|c|c|}
	\hline
	Network & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s & $\alpha,\beta$-Crown-refine & Our method \\ \hline
	& Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s)\\ \hline
	MNIST 6$\times$100 & 57 \hfill 6.9 & 55 \hfill 18.9 & 50 \hfill 1026.1 & 13 \hfill 91.7 & Rate \hfill Time \\ \hline
	MNIST 6$\times$200 & 50 \hfill 6.5 & 47 \hfill 16.6 & 46 \hfill 930.3 & 9 \hfill 79.8 & Rate \hfill Time \\ \hline
	MNIST 9$\times$100 & 63 \hfill 7.2 & 58 \hfill 20.1 & 58 \hfill 1162.9 & 21 \hfill 102.2 & Rate \hfill Time \\ \hline
	MNIST 9$\times$200 & 56 \hfill 6.8 & 55 \hfill 18.2 & 54 \hfill 1083.1 & 16 \hfill 83.2 & Rate \hfill Time \\ \hline
	0 & 0 & 0 & 0 & 0 & 0 \\ \hline
\end{tabular}
